%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Research Scientist, Computational Biology}
{Gubra}
{Hørsholm, Denmark}
{2021-05 to present}
{
\begin{cvitems}
\item {I am contributing to preclinical research and drug discovery at Gubra, where I am responsible for the data and app infrastructure in our drug discovery platform.}
\item {Digitalisation of internal discovery processes and customer facing services, through Shiny applications and robust data-informed processes.}
\item {Building a robust and scalable backend for the peptide drug discovery platform and making data available to users and scientists through web apps and APIs.}
\item {Building a pipeline for potency data analysis. I ensured automatic and uniform treatment so results were comparable across hundreds of experiments and made results easily available for downstream processes.}
\item {Building a pipeline for summarising and analysing mass spectrometry data for use in drug discovery.}
\item {Applying Large Language Models (LLMs) to peptide design.}
\end{cvitems}
}

\cventry
{Data Scientist} % Job title
{Novo Nordisk} % Organization
{Hillerød, Denmark} % Location
{2017-09 to 2021-04} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Increasing overall equipment efficiency of an assembly line by applying a combination of Design of Experiments and Gaussian Processes Regression and Bayesian optimisation. Skills applied: ML, A/B testing, Python, Bayesian statistics.}
\item {Predictive maintenance on brownfield manufacturing equipment.Skills used: AWS Greengrass, AWS IoT, CI/CD with Azure DevOps}
\item {Digital transformation of 3 factories through fast-paced prototyping and development of data based products. One of these factories is recognised as a Digital Lighthouse Factoryby the World Economic Forum. Skills appied: Agile/Scrum, data visualisation, optimisation.}
\item {Creating dashboards for planning in factories. Skills applied: Docker, Tableau, Streamlit, InfluxDB, visualisation, Python.}
\item {We built a regulatory framework for applying machine learning to quality-critical pharma processes. Skills applied: GxP, models in production, model validation, model monitoring.}
\item {Involved in hiring 15+ data professionals, personally leading 100+ interviews.}
\item {I started out in Supply Chain where I applied data and occasionally machine learning to simplify processes and understand trends while maintaining SQL databases.}
\item {From 2019-02, I helped establish a Manufacturing Intelligence department. We applied modern data technology to manufacturing problems while advocating data science and machine learning within the organisation. My responsibilities were quite diverse ranging from data engineering tasks and coming up with machine learning cases to teaching colleagues and hiring.}
\end{cvitems}
}

\cventry
{Intern}
{Innovation Centre Denmark, Embassy of Denmark to South Korea}
{Seoul, South Korea}
{2016-08 to 2017-01}
{
\begin{cvitems}
\item {Collected market intelligence, facilitated Korean-Danish technology collaboration, arranged and executed large events, and had various diplomatic tasks.}
\end{cvitems}
}
%------------------------------------------------

\end{cventries}