%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

%------------------------------------------------

\cvskill
{Programming \& Scripting} % Category
{I have been writing \textbf{Python} for 6+ years and I am comfortable with several common data manipulation libraries. I also have 2+ years of experience writing \textbf{R}, using \textbf{Shiny} to build apps and Plumber to build \textbf{API}s. I am \textbf{Unix}-savvy and used to work in command-line environments.} % Skills

%------------------------------------------------

\cvskill
{Machine Learning / AI} % Category
{I have a solid theoretical understanding of ML and deep learning methods, as well as 5+ years of experience applying them to various domains. I have applied ML to solve complex problems, often with sparse or little data. Toolbox: \textbf{Stan}, \textbf{LLMs}, \textbf{SciKit}, \textbf{Pytorch}, etc.} % Skills

%------------------------------------------------

\cvskill
{Databases \& SQL}
{I have been developing and using databases for 5+ years. I am comfortable with multiple dialects of SQL, though mostly \textbf{MSSQL} and \textbf{Postgres}.I have designed and built databases for \textbf{production} from scratch on multiple occasions. I have NoSQLexperience too, mostly \textbf{DynamoDB}.}

\cvskill
{Statistics}
{I have a strong theoretical understanding of classical statistics and experience applying Bayesianand multivariate statistics, including ML methods like Gaussian Processes. I have experience implementing statistical workflows in R and Stan.}

\cvskill
{Computational Biology}
{Metagenomics, Peptide Design, NGS}

\cvskill
{Developer Tools}
{Docker, Git, CI/CD with Azure DevOps, Agile/Scrum}

\cvskill
{AWS}
{Certified SAA, IoT, S3, EC2, ECS, Kinesis, DynamoDB etc.}


\cvskill
{Languages} % Category
{Fluent in Danish, English, and Korean} % Skills

%------------------------------------------------

\end{cvskills}